Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2021-01-10 paper/paper.Rmd
Adding skeleton figures

---
title: "Individual Variation in Animal Movement and Effects on Seed Dispersal Distance"
abstract: |
  I don't like this abstract. Revisit at the end...Seed dispersal is a fundamental process in plant ecology and due to its high importance in the ecosystem, various modelling approaches have been developed to understand seed movement and dispersal mechanisms. In particular, long-distance seed dispersal (LDD) plays a significant role in determining a population's genetic diversity and range expansion. Animal-mediated seed dispersal is a key component of LDD events, as frugivores can travel long distances and transport seeds with them. In this study we seek to understand the implications of individual variation in animal movement and how these can impact estimates of long distance seed dispersal. We apply these methods to empirical data sets that contain locations for an araçari, *Pteroglossus pluricintus*, one of the primary frugivores for the Amazonian canopy tree *Virola flexuosa*. We combine animal movement data and gut retention time to simulate *Virola* seed dispersal. This approach showed that there is significant variation in individual araçari movement patterns which directly influence the estimated number of long-distance dispersal events for *Virola* seeds. We found that models that ignore this underlying variation in individual animal movement, underestimate the percentage of long-distance seed dispersal events and maximum seed dispersal distances.
output:
  word_document:
    reference_docx: paper_ref.docx
  html_document:
    df_print: paged
bibliography: mybibfile.bib
---

@@

We calculated seed dispersal distance as the euclidean distance of each seed to the parent plant. Given that our models only considered one parent plant located at the origin per simmulation, we calculated seed dispersal distance (DD) as the distance from each seed's location to the origin as follows:
$$DD_i = \sqrt{(0-x_i)^2 + (0-y_i)^2} $$
where $DD_i$ is the dispersal distance for seed $i$ in the simulation run and $x_i$ and $y_i$ are its xy coordinates in the landscape. We also used an aggregation metric to determine how evenly seeds would be dispersed across the landscape, and calculated seed dispersion (SD) as the average distance of each seed to the mean seed location in each simulation run (following methods in [@jones_closing_2017]):
$$SD = \frac{\sum \sqrt{(x_m - x_i)^2 + (y_m - y_i)^2}}{n}$$
where $n$ is the number of seeds for each simulation run (5), and $x_m$ and $y_m$ is the mean seed location in the simulation run. The information on seed dispersal distance was used for the toucan-generated seed dispersal kernels for each one of our models (null, individual, and family group), and these seed dispersal distances were also classified as long distance dispersal events if they exceeded 500m [@holbrook_using_2007]. The proportion of long-distance dispersal events, maximum dispersal distance, and average seed dispersion were used to compare seed dispersal between our three models of individual variation.

@@

Look into this, but probably use a Weibull distribution like morales and carlo, and then compare the parameters to describe them. An alternative approach would be to use an extreme distribution like the garcia paper to describe this.

@@

@@

>>>>

---
title: "Individual Variation in Animal Movement and Effects on Seed Dispersal Distance"
abstract: |
  I don't like this abstract. Revisit at the end...Seed dispersal is a fundamental process in plant ecology and due to its high importance in the ecosystem, various modelling approaches have been developed to understand seed movement and dispersal mechanisms. In particular, long-distance seed dispersal (LDD) plays a significant role in determining a population's genetic diversity and range expansion. Animal-mediated seed dispersal is a key component of LDD events, as frugivores can travel long distances and transport seeds with them. In this study we seek to understand the implications of individual variation in animal movement and how these can impact estimates of long distance seed dispersal. We apply these methods to empirical data sets that contain locations for an araçari, *Pteroglossus pluricintus*, one of the primary frugivores for the Amazonian canopy tree *Virola flexuosa*. We combine animal movement data and gut retention time to simulate *Virola* seed dispersal. This approach showed that there is significant variation in individual araçari movement patterns which directly influence the estimated number of long-distance dispersal events for *Virola* seeds. We found that models that ignore this underlying variation in individual animal movement, underestimate the percentage of long-distance seed dispersal events and maximum seed dispersal distances.
output:
  html_document:
    df_print: paged
  word_document:
    reference_docx: paper_ref.docx
bibliography: mybibfile.bib
---

@@

We calculated seed dispersal distance as the euclidean distance of each seed to the parent plant. Given that our models only considered one parent plant located at the origin per simmulation, we calculated seed dispersal distance (DD) as the distance from each seed's location to the origin as follows:
$$DD_i = \sqrt{(0-x_i)^2 + (0-y_i)^2} $$
where $DD_i$ is the dispersal distance for seed $i$ in the simulation run and $x_i$ and $y_i$ are its xy coordinates in the landscape. We also used an aggregation metric to determine how evenly seeds would be dispersed across the landscape, and calculated seed dispersion (SD) as the average distance of each seed to the mean seed location in each simulation run (following methods in [@jones_closing_2017]):
$$SD = \frac{\sum \sqrt{(x_m - x_i)^2 + (y_m - y_i)^2}}{n}$$
where $n$ is the number of seeds for each simulation run (5), and $x_m$ and $y_m$ is the mean seed location in the simulation run. The information on seed dispersal distance was used for the toucan-generated seed dispersal kernels for each one of our models (null, individual, and family group), and these seed dispersal distances were also classified as long distance dispersal events if they exceeded 500m [@holbrook_using_2007]. The proportion of long-distance dispersal events, maximum dispersal distance, and average seed dispersion were used to compare seed dispersal between our three models of individual variation (Table1).

@@

- Already fit the weibull distribution for this. I have

@@

```{r}
load("dispersal_kernels.RData")
```

```{r fig.width=6}
plot_grid(
  fam_dispersal %>%
    ggplot(., aes(x = dispersal)) +
    geom_histogram(),
  plot_grid(fam_dispersion %>%
            ggplot(., aes(y = mean_dispersal)) +
            geom_boxplot(),
          fam_dispersion %>%
            ggplot(., aes(y = seed_dispersion)) +
            geom_boxplot()), nrow = 2)
```

@@

## Weibull seed dispersal kernel

**Table 1.**
```{r}

knitr::kable(dispersal_kernel_table)
```
